CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability

### 2019-02-14 gpus/paper.tex

is a compressible (radiation-)hydrodynamics simulation code built on
the AMReX adaptive mesh refinement framework \citep{castro,castro2,castro3}.  It 
includes full self-gravity using multigrid methods with isolated boundaries
\cite{katz:2016}, works with general equations of state \citep{zingalekatz}
and arbitrary nuclear reaction networks.

Existing GPU-enabled astrophysical hydro codes include
\citet{gamer,cholla,fargo3d,pekkila:2017,caplan:2018,racz:2018,liska:2018,goz:2018}

@@

@@

Discuss open development model

>>>>

\castro\ is a compressible (radiation-)hydrodynamics simulation code built on
the AMReX adaptive mesh refinement framework \citep{castro,castro2,castro3}.  It 
includes full self-gravity using multigrid methods with isolated boundaries
\citep{katz:2016}, works with general equations of state \citep{zingalekatz}
and arbitrary nuclear reaction networks.  Castro has been used for science investigations of
...

The original computing architectures targeted were

With GPU accelerators becoming increasingly dominant, algorithms need to be ported.
There are a number of descriptions of GPU-enabled astrophysical hydro codes, including
\citet{gamer,cholla,fargo3d,pekkila:2017,caplan:2018,racz:2018,liska:2018,goz:2018}

@@

In this paper, we describe our approach to performance portability.
Our goal is to have the same computational kernels run efficiently on
CPUs (including manycore processors) and GPUs.  We describe the work
we needed to do to enable this portability and show performance
metrics for a reacting flow problem in astrophysics.

@@

\castro\ is developed using a fully open-development model, with the
code managed in git and hosted on
github\footnote{\url{https://github.com/amrex-astro/Castro/}}.
Contributions from the community are welcomed via github issues and
pull requests.  For the science projects that the core development
team are working on, all problem setup, input files, auxillary data,
and anything else needed for the science is stored in the main github
repo, allowing for the community to contribute to the science and
reproduce results as they are published.
